### 2015-08-14 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
updated text

%%%
%%% SUBSECTION
%%%
\subsection{Motivation and Objectives}
\CO\; has been injected in underground geological formations to enhance hydrocarbon productivity (e.g. \CO-EOR) whilst disposing acidic gasses (mainly H$_{2}$S and \CO) from natural occurance or captured from industrial plants. This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions. However, geological \CO\; storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
\begin{enumerate}[(a)]
   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
   \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
   \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e} 
\end{enumerate}

Although the main focus of this proposal is to assess potential \CO\; leakage (\ref{options:d}), the technology developed here can also be applied to assess the storage feasibility of new and existing geological sites (\ref{options:b},~\ref{options:c}).  Risk assessment based on detailed numerical simulations can identify specific risk features and processes (e.g., leaky faults and wellbores, unexpected injection pressure rise, residual saturation trapping) which may help prevent unintended CO2 migration. Our model framework may also be used during the continuous site monitoring stage (\ref{options:e}) to assess potential risks during injection and storage as the model can use data from field sensors (data assimilation) to help predict the likelihood of \CO\; leakage.

>>>>

%%%
%%% SUBSECTION
%%%
\subsection{Motivation and Objectives}
\CO\; has been injected in underground geological formations to enhance hydrocarbon productivity (e.g. \CO-EOR). %whilst disposing acidic gasses (mainly H$_{2}$S and \CO) from natural occurance or captured from industrial plants. 
This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions. However, geological \CO\; storage schemes must comply with UK/EUrequirements (European Council's directive 2009/31/EC) for:
\begin{enumerate}[(a)]
%
   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
%
   \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
%
   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
%
   \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
%
   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e} 
%
\end{enumerate}

Although the main focus of this proposal is to assess potential \CO\; leakage (\ref{options:d}), the technology developed here can also be applied to assess the storage feasibility of new and existing geological sites (\ref{options:b},~\ref{options:c}).  Risk assessment based on detailed numerical simulations can identify specific risk features and processes (e.g., leaky faults and wellbores, unexpected injection pressure rise, residual saturation trapping) which may help prevent unintended \CO\; migration. Our model framework may also be used during the continuous site monitoring stage (\ref{options:e}) to assess potential risks during injection and storage as the model can use data from field sensors (data assimilation) to help predict the likelihood of \CO\; leakage.

The main objectives of this proposal are:
\begin{enumerate}[(i)]
%
   \item Investigation of \CO\; plume dynamics (migration and leakage);
%
   \item Assessment of fluid flow through zones of potential rheological weakness in the overburden (e.g., faults and chimneys);
%
   \item    
%
\end{enumerate}
